Automated Lensing Learner - I: An automated Strong Lensing Identification Pipeline

### 2017-03-23 ms.tex
Final edits before circulating

% Train time behavior for LSST1 and nLSST1
\wording{For LSST1, Figure~\ref{fig:traintimeLSST1} shows the same
  relationships between train time and train size in blue, and the
  optimal regulariztion parameter (or model complexity) in red.
  Contrary to what we found when comparing LSST10 to nLSST10, nLSST1
  requires more model complexity than LSST1.  Recall that LSST1 and
  nLSST1 correspond to single epoch simulated exposures with the best
  seeing; these images exhibit better resolution but worse signal to
  noise.  The switch in required model complexity corresponds to a
  trade-off between features from the lens galaxy providing additional
  information or swamping the signal from a strong lensing arc.}

>>>>

% Train time behavior for LSST1 and nLSST1
For LSST1, Figure~\ref{fig:traintimeLSST1} shows the same
relationships between train time and train size in blue, and the
optimal regulariztion parameter (or model complexity) in red.
Contrary to what we found when comparing LSST10 to nLSST10, nLSST1
requires more model complexity than LSST1.  Recall that LSST1 and
nLSST1 correspond to single epoch simulated exposures with the best
seeing; these images exhibit better resolution but worse signal to
noise.  The switch in required model complexity corresponds to a
trade-off between features from the lens galaxy providing additional
information or swamping the signal from a strong lensing arc.
